\LARGE \bf Informed sampling by Markov Chain Monte Carlo methods

### 2017-03-02 paper.tex
future work
?

One of the popular classes of Monte Carlo simulation is 
\emph{Markov Chain Monte Carlo} (MCMC)~\cite{ADDJ03}.
Here, the samples are drawn by generating a Markov chain such that the distribution of points on the chain converges to the desired distribution.
The Markov Chain can be generated by performing a random walk such as
in Metropolis-Hastings~\cite{CG95} or Gibbs sampling~\cite{CK94}.
Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N94} (instead of performing the random walk).
This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{N11} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.

@@

\appendix
\section{HMC}
%base on https://theclevermachine.wordpress.com/2012/11/18/mcmc-hamiltonian-monte-carlo-a-k-a-hybrid-monte-carlo/

@@

To explore the entire space, the dynamics are randomly perturbed. This is done by drawing a random momentum from $\pi(q)$ before running the dynamics prior to each sampling iteration $t$. Combining these steps, sampling random momentum, followed by Hamiltonian dynamics and Metropolis acceptance criterion defines the HMC algorithm.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Old text that may be re-used
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ignore{
In order to take advantage of these powerful methods, we propose to reformulate the cost surface as a probability density. Specifically, we consider a Boltzmann distribution in order to formulate the cost function using flexible energy based methods. Because Monte Carlo methods only consider the ratio of the probabilities, we do not need to consider the problem of estimating the intractable partition function.

>>>>

One of the popular classes of Monte Carlo simulation is 
\emph{Markov Chain Monte Carlo} (MCMC)~\cite{ADDJ03}.
Here, the samples are drawn by generating a Markov chain such that the distribution of points on the chain converges to the desired distribution.
The Markov Chain can be generated by performing a random walk such as
in Metropolis-Hastings~\cite{CG95}, 
Gibbs sampling~\cite{CK94},
hit-and-run~\cite{S84,KSZ11} and their many variants.
Alternatively, samples on the chain can be generated by simulating Hamiltonian dynamics~\cite{N94} (instead of performing the random walk).
This approach, termed Hybrid or Hamiltonian Monte Carlo (HMC)~\cite{N11} was shown to converge faster to the desired distribution, when compared to random-walk based MCMC algorithms.

@@

estimating volume of informed space

%\appendix
\appendices
\section{HMC}
%base on https://theclevermachine.wordpress.com/2012/11/18/mcmc-hamiltonian-monte-carlo-a-k-a-hybrid-monte-carlo/

@@

To explore the entire space, the dynamics are randomly perturbed. This is done by drawing a random momentum from $\pi(q)$ before running the dynamics prior to each sampling iteration $t$. Combining these steps, sampling random momentum, followed by Hamiltonian dynamics and Metropolis acceptance criterion defines the HMC algorithm.

\section{Gibbs sampling and Hit-and-run}
Gibbs sampling is a simple MCMC algorithm which samples each dimension (or variable) from its \emph{conditional distribution} with the remaining variables fixed to their current values.
Specifically,

%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Old text that may be re-used
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\ignore{
In order to take advantage of these powerful methods, we propose to reformulate the cost surface as a probability density. Specifically, we consider a Boltzmann distribution in order to formulate the cost function using flexible energy based methods. Because Monte Carlo methods only consider the ratio of the probabilities, we do not need to consider the problem of estimating the intractable partition function.
